---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DTComPair

  <!-- badges: start -->
  [![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
  [![CRAN status](https://www.r-pkg.org/badges/version/DTComPair)](https://CRAN.R-project.org/package=DTComPair)
  <!-- badges: end -->

Comparison of the accuracy of two binary diagnostic tests in a "paired" study design, i.e. when each test is applied to each subject in the study.


## Installation

**CRAN**

You can install the current stable version from CRAN with:

```{r cran-installation, eval = FALSE}
install.packages("DTComPair")
```

**GitHub**

You can install the current development version from GitHub with:

```{r gh-installation, eval = FALSE}
if (!require("remotes")) {install.packages("remotes")}
remotes::install_github("chstock/DTComPair")
```

## Getting Started

**Determine the accuracy of one diagnostic test**

```{r getting-started1}
library(DTComPair)
data(Paired1) # Hypothetical study data
a1 <- tab.1test(d=d, y=y1, data=Paired1)
print(a1)
a2 <- acc.1test(a1)
print(a2)
```

**Compare the accuracy of two diagnostic tests**
```{r getting-started2}
b1 <- tab.paired(d=d, y1=y1, y2=y2, data=Paired1)
print(b1)
b2 <- acc.paired(b1)
print(b2)
```


## Citing `DTComPair`

To cite `DTComPair` in publications please use: Stock C, Hielscher T, Discacciati A (2023). DTComPair: comparison of binary diagnostic tests in a paired study design. R package, version 1.2.0. URL: https://CRAN.R-project.org/package=DTComPair.



